Hello OpenScPCA

### 2024-03-18 analyses/hello-R/hello.Rmd
Move notebook out of subdirectory

Set the paths to the data, results, and plots directories.

@@

We will be creating two output files: a table and a plot.
Defining their locations in the `Setup` section will make it easy for future notebook users to know what to expect.

@@

```{r}
# function to count cells in an sce file
# returns a data frame with ids and cell count
count_sce <- function(sce_file) {
  # load the SCE object
  sce <- readRDS(sce_file)

>>>>

Set the paths to the data, results, and plots directories.
Here we use the `rprojroot` package to find:

- the root of the `OpenScPCA-analysis` repository by looking for the (hidden) `.git` directory.
- the root of this module by looking for the `renv.lock` file.

Then we define the directories for input data and output results based on those root directories.

@@

We will be creating two output files: a table and a plot.
Defining their locations in the `Setup` section will make it easy for future users (including us in the future) to know what to expect as output from this notebook.

@@

```{r}
count_sce <- function(sce_file) {
  # function to count cells in an sce file
  # returns a data frame with the following columns:
  # - project_id
  # - sample_id
  # - library_id
  # - n_cells: number of cells in the library

  # load the SCE object
  sce <- readRDS(sce_file)

  # input check
  stopifnot("`sce_file` must contain a SingleCellExperiment object" = is(sce, "SingleCellExperiment"))
